Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-07-11 manuscripts/manuscript1.qmd
stuff

```{r setup}
#| echo: false
#| output: false

library(targets)
library(tidyverse)
library(withr)
library(here)
library(formattable)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)
library(glue)

# plot stuff
theme_ich <- function(base_family = "Figtree",
                      base_size = 14) {
  theme_minimal(base_size = base_size) +
    theme(
      text = element_text(lineheight = 2),
      plot.title = element_text(size = rel(1.3), margin = margin(12, 0, 8, 0)),
      plot.subtitle = element_text(size = rel(1.1), margin = margin(4, 0, 0, 0)),
      axis.text.y = element_text(size = rel(0.8)),
      axis.title.y = element_text(size = rel(0.5), margin = margin(0, 4, 0, 0)),
      axis.text.x = element_text(size = rel(1)),
      axis.title.x = element_blank(),
      legend.position = "bottom",
      legend.justification = 1,
      panel.grid = element_blank(),
      panel.background = element_blank(),
      plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
    )
}

@@

models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neutral_neurosurgery)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_neutral_evd)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_neutral_tracheostomy)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_neutral_days_mechanical_ventilation)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_neutral_comfort)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_neutral_early_wlst)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_neutral_dnr_binary))
)

@@

```{r neurosurgery}
#| label: tbl-2
#| tbl-cap: "Association between hemispheric lateralization and aggressive care"
#| echo: false
#| warning: false

@@

aOR_CIs_combined[1] <- c(
  "Neurosurgical Intervention",
  "External Ventricular Drain",
  "Tracheostomy",
  "Days of Mechanical Ventilation",
  "Withdrawal of Life-Sustaining Therapy",
  "Early Withdrawal of Life-Sustaining Therapy",
  "DNR Order"
)

@@

# combine probability of OR > 1 (prob of difference)
prob_difference <- tibble(
  "Neurosurgical Intervention" = pluck(neurosurgery, 1),
  "External Ventricular Drain" = pluck(evd, 1),
  "Tracheostomy" = pluck(trach, 1),
  "Days of Mechanical Ventilation" = pluck(vent, 1),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 1),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 1),
  "DNR Order" = pluck(dnr, 1)
) |>
  pivot_longer(
    cols = everything(),
    names_to = "Outcome",
    values_to = "Probabilty of any difference (aOR > 1)"
  )

# combine % of posterior within the ROPE
rope <- tibble(
  "Neurosurgical Intervention" = pluck(neurosurgery, 4),
  "External Ventricular Drain" = pluck(evd, 4),
  "Tracheostomy" = pluck(trach, 4),
  "Days of Mechanical Ventilation" = pluck(vent, 4),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 4),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 4),
  "DNR Order" = pluck(dnr, 4)
) |>
  pivot_longer(
    cols = everything(),
    names_to = "Outcome",
    values_to = "% within ROPE"
  )

@@

column_names <- c(
  "Neurosurgical Intervention",
  "External Ventricular Drain",
  "Tracheostomy",
  "Days of Mechanical Ventilation",
  "Withdrawal of Life-Sustaining Therapy",
  "Early Withdrawal of Life-Sustaining Therapy",
  "DNR Order"
)

@@

tibble_2 |>
  fmt_number(columns = 6:7, decimals = 2)

@@

>>>>

```{r setup}
#     axis.text.y = element_text(size = rel(0.8)),
      axis.title.y = element_text(size = rel(0.5), margin = margin(0, 4, 0, 0)),
      axis.text.x = element_text(size = rel(1)),
      axis.title.x = element_blank(),
      legend.position = "bottom",
      legend.justification = 1,
      panel.grid = element_blank(),
      panel.background = element_blank(),
      plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
    )
}

@@

models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neutral_neurosurgery)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_neutral_evd)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_neutral_days_mechanical_ventilation)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_neutral_tracheostomy)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_neutral_comfort)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_neutral_early_wlst)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_neutral_dnr_binary))
)

bob <- ich_aggressive |>
  tabyl(neurosurgery_evac, ich_laterality) |>
  adorn_percentages("col") |>
  adorn_pct_formatting(digits = 1) |>
  adorn_ns(position = "front") |>
  filter(neurosurgery_evac == "Yes")

ich_aggressive |>
  tabyl(days_mechanical_ventilation, ich_laterality)

@@

```{r table 2}
#| label: tbl-2
#| tbl-cap: "Association between hemispheric lateralization and aggressive care"
#| echo: false
#| warning: false

@@

aOR_CIs_combined[1] <- c(
  "Neurosurgical Intervention",
  "External Ventricular Drain",
  "Days of Mechanical Ventilation",
  "Tracheostomy",
  "Withdrawal of Life-Sustaining Therapy",
  "Early Withdrawal of Life-Sustaining Therapy",
  "DNR Order"
)

@@

# combine probability of OR > 1 (prob of difference)
prob_difference <- tibble(
  "Neurosurgical Intervention" = pluck(neurosurgery, 1),
  "External Ventricular Drain" = pluck(evd, 1),
  "Days of Mechanical Ventilation" = pluck(vent, 1),
  "Tracheostomy" = pluck(trach, 1),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 1),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 1),
  "DNR Order" = pluck(dnr, 1)
) |>
  pivot_longer(
    cols = everything(),
    names_to = "Outcome",
    values_to = "Probabilty of any difference (aOR > 1)"
  )

# combine % of posterior within the ROPE
rope <- tibble(
  "Neurosurgical Intervention" = pluck(neurosurgery, 4),
  "External Ventricular Drain" = pluck(evd, 4),
  "Days of Mechanical Ventilation" = pluck(vent, 4),
  "Tracheostomy" = pluck(trach, 4),
  "Withdrawal of Life-Sustaining Therapy" = pluck(wlst, 4),
  "Early Withdrawal of Life-Sustaining Therapy" = pluck(early_wlst, 4),
  "DNR Order" = pluck(dnr, 4)
) |>
  pivot_longer(
    cols = everything(),
    names_to = "Outcome",
    values_to = "% within ROPE"
  )

@@

column_names <- c(
  "Neurosurgical Intervention",
  "External Ventricular Drain",
  "Days of Mechanical Ventilation",
  "Tracheostomy",
  "Withdrawal of Life-Sustaining Therapy",
  "Early Withdrawal of Life-Sustaining Therapy",
  "DNR Order"
)

@@

tibble_2 |>
  fmt_number(columns = 6:7, decimals = 2) |>
  tab_footnote(
    footnote = "Adjusted for: age, admission GCS, ICH location, IVH, and study (as random intercept)",
    locations = cells_column_labels(columns = 4)
  ) |>
  tab_footnote(
    footnote = "Region of Practical Equivalence, defined as 0.95 > aOR > 1.05",
    locations = cells_column_labels(columns = 7)
  )

@@

predictions(models$"Neurosurgical Intervention", by = c("ich_laterality", "study")) |>
  posterior_draws() |>
  ggplot(aes(x = draw, fill = ich_laterality)) +
  geom_density(alpha = .7) +
  facet_grid(~study) +
  scale_fill_manual(values = c("#054224", "#ff8800")) +
  scale_y_continuous() +
  scale_x_continuous(
    limits = c(0, 0.2),
    breaks = seq(0, 0.20, 0.05),
    labels = scales::percent
  ) +
  labs(
    fill = "ICH Laterality",
    y = NULL
  ) +
  theme_ich()

models$"Neurosurgical Intervention" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  ggplot(aes(ich_right_or)) +
  # geom_density(color = "#054224", fill = "#ff8800") +
  stat_halfeye(aes(fill_ramp = after_stat(x > 1.05 | x < 0.95), fill = "#E69F00", color = "#422f05")) +
  scale_x_continuous(breaks = seq(0, 3, 0.25)) +
  labs(
    title = "aOR Neurosurgical Intervention - Right Hemisphere",
    y = NULL,
    fill = NULL
  ) +
  geom_vline(
    xintercept = 1, linetype = "dashed",
    color = "#999999", linewidth = 1
  ) +
  geom_vline(
    xintercept = 1.05, linetype = "dotted",
    color = "#999999", linewidth = 1
  ) +
  geom_vline(
    xintercept = 0.95, linetype = "dotted",
    color = "#999999", linewidth = 1
  ) +
  theme_ich() +
  theme(legend.position = "none")

models$"External Ventricular Drain" |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  ggplot(aes(ich_right_or)) +
  # geom_density(color = "#054224", fill = "#ff8800") +
  stat_halfeye(aes(fill_ramp = after_stat(x > 1.05 | x < 0.95), fill = "#E69F00", color = "#E69F00")) +
  scale_x_continuous(
    breaks = seq(0, 3, 0.25)
  ) +
  labs(
    title = "aOR Ventriculostomy - Right Hemisphere",
    y = NULL,
    fill = NULL
  ) +
  geom_vline(
    xintercept = 1, linetype = "dashed",
    color = "#999999", linewidth = 1
  ) +
  geom_vline(
    xintercept = 1.05, linetype = "dotted",
    color = "#999999", linewidth = 1
  ) +
  geom_vline(
    xintercept = 0.95, linetype = "dotted",
    color = "#999999", linewidth = 1
  ) +
  theme_ich() +
  theme(legend.position = "none")

### 2024-07-11 manuscripts/manuscript1_supplement.qmd
stuff

library(targets)
library(tidyverse)
library(withr)
library(here)
library(modelsummary)
library(marginaleffects)
library(brms)
library(tidybayes)
library(bayesplot)
library(glue)
library(ggdist)
library(patchwork)
library(tinytable)
library(gt)

@@

```{r dags}
#| echo: false

# dag_aggressive

@@

>>>>

library(targets)
library(tidyverse)
library(withr)
library(here)
library(ggdag)
library(modelsummary)
library(marginaleffects)
library(brms)
library(tidybayes)
library(bayesplot)
library(glue)
library(ggdist)
library(patchwork)
library(tinytable)
library(gt)

@@

```{r dags}
#| echo: false
#| warning: false
#| fig-height: 8

with_dir(here(), tar_load(dag_aggressive))

status_colors <- c(exposure = "#0074D9", outcome = "#FF4136", latent = "grey50")

dag_aggressive |>
  tidy_dagitty() |>
  node_status() |>
  ggdag() +
  geom_dag_edges() +
  geom_dag_point(aes(color = status)) +
  geom_dag_label_repel(aes(label = label, fill = status),
    seed = 1234,
    color = "white", fontface = "bold"
  ) +
  scale_color_manual(values = status_colors, na.value = "grey20") +
  scale_fill_manual(values = status_colors, na.value = "grey20") +
  guides(color = "none", fill = "none") +
  theme_dag()

@@

### Different Priors

### Alternative Adjustment Sets

### Alternative Handling of Missing Data
